---
title: "Misadventures with Reproducibility in R"
subtitle: "R Ladies Melbourne, 29 Nov 2022"
author: "[Cynthia Huang](https://twitter.com/cynthiahqy)"
format:
  rladies-revealjs:
    footer: "[R-Ladies](https://rladies.org/) theme for [Quarto Presentations](https://quarto.org/docs/presentations/revealjs/index.html). Code available on [GitHub](https://github.com/beatrizmilz/quarto-rladies-theme)."
    slide-number: true
    preview-links: auto
incremental: false
embed-resources: true
---

```{r setup}
library(gt)
library(dplyr)
```

## About Me

<!--# can I just iframe my website? -->

## Itinerary

### Surveying the Tools Landscape

### My Journey with Reproducibility

### What about you?

### Tips for Choosing your Own Adventure


## Reproducibility! Now!

![An illustration of reasons why we should care about working reproducibly. [Fig 7, Guide for Reproducible Research, The Turing Way](https://the-turing-way.netlify.app/reproducible-research/overview/overview-benefit.html)](https://the-turing-way.netlify.app/_images/reasons-reproducibility.png)

## An ever growing pile of tools...

```{r gt-pkgs}
tribble(~pkg, ~type, ~hex_url, ~pkg_website,
        "renv", "computational environments", "https://raw.githubusercontent.com/rstudio/renv/757754bed853e421dfe7ea38b52dc59141e87ce2/man/figures/logo.svg", "https://rstudio.github.io/renv/",
        "litr", "literature programming", "https://github.com/jacobbien/litr-project/blob/0838ca81ef705ed8f706f40f7a8bbfff8a21f353/litr/man/figures/logo.png?raw=true", "https://jacobbien.github.io/litr-project/"
        #"quarto", "authoring frameworks", "link", "https://quarto.org"
) |>
  #mutate(hex_button = glue::glue('<a href="{pkg_docs}"><img src="{hex_url}"></a>')) |>
  mutate(hex_button = sprintf('<a href="%s"><img src="%s" style="height:35px"></a>', pkg_website, hex_url)) |>
  mutate(hex_button = purrr::map(hex_button, gt::html)) |>
  select(pkg, hex_button) |>
  gt()
```

# Mapping my Journey

## some context...

-   majored in economics at Unimelb -- no coding! very little econometrics... mostly theory..
-   taught myself to code in R & python while working as a research assistant at UniMelb
-   designed, collected, wrangled and explored all sorts of wild caught data -- surveys, archives, time-series, spatial, panel, text...
-   dabbling with modelling..

## {background-image="images/map-blank.png" background-size="contain"}

## Wandering the forest {background-image="images/map-beginner.png" background-size="contain"}

## Up into the Clouds {background-image="images/map-intermediate.png" background-size="contain"}

## Out to Sea {background-image="images/map-advanced.png" background-size="contain"}

------------------------------------------------------------------------

-   command line interface
-   literature programming, authoring frameworks
-   version control
-   collaboration
-   "you should check this out"

# What about you?

------------------------------------------------------------------------

::: columns
::: {.column width="40%"}
Menti-Meter
:::

::: {.column width="60%"}
Enablers - Life changing tools? -

Frictions - Things you "should" do, but just can't -
:::
:::

------------------------------------------------------------------------

# Choose your Own Adventure

## Lessons from my misadventures

-   Invest in the command line
-   

## Thanks for listening!
